---
title: "Preliminary Results for West Region by Depth"
author: "Ben Best"
date: |
  | `r format(Sys.time(), '%Y-%m-%d')`
output:
  html_document:
    toc: yes
    toc_depth: '4'
  bookdown::word_document2:
    toc: yes
    toc_depth: 4
  bookdown::html_document2:
    self_contained: no
    toc: yes
    toc_float: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    toc: yes
---

Here are preliminary results of the form (table, plot, map) to be output with many more layers and for each of the 8 regions: 

1. Alaska
1. Atlantic Islands
1. East
1. Great Lakes
1. Gulf of Mexico
1. Hawaii
1. Pacific Islands
1. West

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(rmarkdown)
library(bookdown)
library(glue)
library(raster)
#library(tabularaster)
library(formattable)
library(htmltools)
#library(kableExtra)
library(DT)
library(leaflet)
devtools::load_all("~/github/nrelutils") # devtools::install_github("ecoquants/nrelutils"); library(nrelutils) 
select <- dplyr::select

knitr::opts_chunk$set(warning=F, message=F, eval=T, echo=F, cache=F) # DEBUG
#knitr::opts_chunk$set(echo=F) # DEBUG
```

## Table

```{r tblTerDepth, eval=T}
setwd("~/github/nrel-uses/prep")

tbl_cat <- readxl::read_xlsx("~/github/nrel-uses/data/categories_and_datasets.xlsx", sheet="datasets")

params <- suppressMessages(read_csv('./prep_params.csv'))
#keys_resource <- c("wind", "wave", "tide")
#keys <- setdiff(params$key, keys_resource)
keys <- sort(params$key)

# TODO: for (ter in territories){...}
ter <- "West" # "Alaska"

if (exists("s")) rm(s)
for (key in keys){ # key <- "mpa" # keys[1] "efh" mpa" "wind"
  #cat(glue("{key}"),"\n")

  digest_txt <- glue("./data/{key}/{ter}_{key}_epsg4326.txt")
  
  if (suppressMessages(read_lines(digest_txt)[1]) == "0"){
    #cat(glue("  0, skipping"),"\n")
    next
  }
  
  df <- suppressMessages(read_delim(digest_txt, ":", col_names = c("name","path"))) %>%
    mutate(
      name = ifelse(name == key, name, glue("{key}_{name}")),
      #name = glue("{key}_{name}"),
      path = glue("./data/{key}/{path}"))
  s1 <- stack(as.list(df$path))
  names(s1) <- df$name
  
  #cat(" ", paste0(df$name, collapse="\n  "),"\n")

  if (!exists("s")){
    s <- s1
  } else {
    s <- stack(s, s1)
  }
}

# add area
s <- stack(s, raster::area(s))
names(s)[nlayers(s)] <- "area_km2"

tbl_s <- as.data.frame(s) %>% 
  as_tibble() # 3,241,056 rows for West

# table by depth ----

breaks_depth <- c(0, 100, 200, 1000)
# TODO: inland sliver pixels outside EEZ?, eg WA
lyrs_rm <- c("depth", "wind")

svg_bar <- function(pct, val){
  pct <- ifelse(is.na(pct), 0, round(pct * 100, 3))
  #cat("val before", val,"\n")
  val <- ifelse(is.na(val), "0", as.character(comma(val, digits = 0)))
  #cat("val after", val,"\n")
  glue('
<svg xmlns="http://www.w3.org/2000/svg" version="1.1" width="100%" height="14px" preserveAspectRatio="xMaxYMin meet">
  <g>
    <rect width="{pct}%" height="16" fill="DarkGray"></rect>
    <text text-anchor="end" x="100%" y="12">{val}</text>
  </g>
</svg>
')
  # <text text-anchor="end" x="100%" y="11" font-family="Courier New" font-size="14px" color="black">{val}</text>
}

# depth total
tbl_dt <- tbl_s %>%
  mutate(
    depth_cat = cut(depth, breaks_depth, labels = c("Low", "Medium", "High"), include.lowest = T)) %>% 
  filter(
    !is.na(depth_cat)) %>% 
  group_by(depth_cat) %>%
  summarise(
    area_km2 = sum(area_km2)) %>%
  spread(depth_cat, area_km2) %>%
  mutate(
    Total = sum(Low, Medium, High, na.rm=T))
tbl_dtc <- tbl_dt
names(tbl_dtc) <- glue("{names(tbl_dtc)}_ALL")

# depth
tbl_d <- tibble(
  key      = "depth",
  title    = "Total Area",
  sublayer = "") %>%
  bind_cols(tbl_dt) %>%
  bind_rows(
    tbl_s %>%
      mutate(
        depth_cat = cut(depth, breaks_depth, labels = c("Low", "Medium", "High"), include.lowest = T)) %>%
      filter(
        !is.na(depth_cat)) %>% 
      select(-one_of(lyrs_rm)) %>%
      gather(key = layer, value = value, -depth_cat, -area_km2) %>%
      filter(!is.na(value)) %>%
      group_by(layer, depth_cat) %>%
      summarise(
        area_km2 = sum(area_km2)) %>%
      spread(depth_cat, area_km2) %>%
      rowwise() %>%
      mutate(
        Total = sum(Low, Medium, High, na.rm=T)) %>%
      mutate(
        key      = str_replace(layer, "(.*)_(.*)", "\\1"),
        sublayer = ifelse(
          key == layer, "",
          str_replace(layer, "(.*)_(.*)", "\\2") %>% str_replace_all("\\.", " "))) %>%
      left_join(
        params %>%
          select(key, title), 
        by = "key")) %>%
  cbind(tbl_dtc) %>%
  mutate(
    Low_svg    = map2_chr(Low    / Low_ALL   , Low   , svg_bar),
    Medium_svg = map2_chr(Medium / Medium_ALL, Medium, svg_bar),
    High_svg   = map2_chr(High   / High_ALL  , High  , svg_bar),
    Total_svg  = map2_chr(Total  / Total_ALL , Total , svg_bar))

hdr = withTags(table(
  class = "display",
  thead(
    tr(
      th(colspan=3, "Ocean Use"),
      th(colspan=5, HTML("Area (km<sup>2</sup>) by Depth (m)"))),
    tr(
      th("Category"),
      th("Layer"),
      th("Component"),
      th("0-100m"),
      th("100-200m"),
      th("200-1,000m"),
      th("Total"),
      th("Rank")))))

i_tbl <- 1
caption <- HTML(glue('Table {i_tbl}: Area of Ocean Use (km<sup>2</sup>) by Depth bin (m) for {ter} region. Width of gray horizontal bars from left of cell indicate percent area occupied in given depth bin.'))

tbl_d %>%
  left_join(
    tbl_cat %>%
      select(key, use), 
    by="key") %>%
  arrange(use, title, sublayer) %>%
  mutate(
    rank = dense_rank(1/Total)) %>%
  select(
    Category  = use, 
    Layer     = title, Sublayer = sublayer, 
    `0 - 100` = Low_svg, `100 - 200` = Medium_svg, `200 - 1,000` = High_svg, Total = Total_svg,
    Rank      = rank) %>%
  datatable(
    escape    = F,
    rownames  = F,    
    container = hdr,
    caption   = caption,
    options   = list(
      dom='t',
      pageLength = nrow(tbl_d), 
      ordering=F,
      autoWidth = TRUE,
      columnDefs = list(
        list(width     = '80px'   , targets = 3:6),
        list(className = 'dt-right', targets = 3:7))))
```

## Plot

```{r figTerDepth, fig.cap="Area of Cumulative Ocean Use by Depth Bin for West region. Cumulative use are counted and summarized by depth bin and area. Rank sorts from highest (Total Area of depth bin) to smallest Total area occupied for each layer.", eval=T}
# table of depth for figure
tbl_df <- tbl_s %>%
  mutate(
    depth_cat = cut(depth, breaks_depth, labels = c("0-100", "100-200", "200-1,000"), include.lowest = T)) %>% 
  filter(
    !is.na(depth_cat))
cols_tally <- setdiff(names(tbl_df), c("depth", "depth_cat", "wind", "area_km2"))
tbl_df$tally <- apply(tbl_df[, cols_tally], 1, function(x) sum(!is.na(x)))
tbl_df2 <- tbl_df %>%
  group_by(depth_cat, tally) %>%
  summarise(
    area_km2 = sum(area_km2)) %>%
  #ungroup() %>%
  #mutate(
  #  depth_cat = as.character(depth_cat)) %>%
  # bind_rows(
  #   tbl_df %>%
  #     mutate(
  #       depth_cat = "All") %>%
  #     group_by(depth_cat, tally) %>%
  #     summarise(
  #       area_km2 = sum(area_km2))) %>%
  filter(tally>0)
#View(tbl_df2)

ggplot(data = tbl_df2, aes(x = depth_cat, y = area_km2, fill = tally)) + 
  geom_col() +
  scale_fill_distiller(palette = "Spectral", name="Count") +
  labs(x = "Depth (m)", y = expression(Area (km^2)))
```

## Map

```{r mapTerDepth, fig.cap='Map of cumulative ocean use in West region.', eval=T}
#names(s)
lyrs_rm <- c("depth","wind","area_km2")
s_cnt <- dropLayer(s, which(names(s) %in% lyrs_rm))
r_cnt = sum(!is.na(s_cnt), na.rm=T) %>%
  mask(raster(s, "depth"))
#plot(raster(s, "depth"))
r <- raster_unwrap(r_cnt)
#plot(r)

r_3857 <- projectRasterForLeaflet(r)

vals <- getValues(r_3857)
pal <- colorNumeric(
  palette = 'Spectral', na.color="#00000000", 
  reverse=T, domain = vals)

leaflet(
    options=c(leafletOptions(), attributionControl=F, zoomControl=F, worldCopyJump=T)) %>%
    addProviderTiles("Stamen.TonerLite", group = "B&W") %>%
    addRasterImage(r_3857, project=F, colors=pal, opacity=0.8) %>%
    addGraticule() %>% # interval=1
    addScaleBar('bottomleft') %>%
    addLegend('bottomright', pal, vals, opacity=0.8, title="Count")
```

TODO:

- contours of depth bins for map.

- zoom in for West (NOTE: 2x-clicking on html zooms)

- corresponding table/plot of "Area (km^2) by Tide/Wave/Wind" and map with contours of energy bins.

```{r energy, eval=F}

# table by energy ----
# TODO: for (energy in c("tide","wave","wind")){...}

# limited to a maximum depth (tidal: < 100 m; wave: < 200 m; wind: < 1000 m) and minimum energy classes (tidal: > 500 W/m2; wave: > 10 kW/m; wind > 7 m/s)
limits <- list(
  tide = list(
    break_min = c(500, 1000, 1500),
    break_labels = c("500 - 1,000", "1000 - 1,500", ">1,500"),
    depth = list(
      min = 0,
      max = 100)),
  wave = list(
    break_min = c(10, 20, 30),
    break_labels = c("10 - 20", "20 - 30", ">30"),
    depth = list(
      min = 0,
      max = 200)),
  wind = list(
    break_min = c(7,8.5,10),
    break_labels = c("7 - 8.5", "8.5 - 10", ">10"),
    depth = list(
      min = 0,
      max = 1000)))

energy     <- "wind"
tbl_e      <- tbl_s
tbl$energy <- tbl[[energy]]
lims       <- limits[[energy]]

tbl_e <- tbl_e %>%
  filter(
    energy >= lims$break_min[1],
    depth  >= lims$depth$min,
    depth  <= lims$depth$max,
    !is.na(energy),
    !is.na(depth)) %>% 
  mutate(
    energy_cat = cut(energy, c(lims$break_min, Inf), include.lowest = T))

totals <- tbl %>% 
  group_by(energy_cat) %>%
  summarise(
    area_km2 = sum(area_km2))

tbl_long <- tbl %>% 
  select(-energy, -depth, -wind) %>% 
  gather(key = layer, value = value, -energy_cat, -area_km2) %>%
  filter(!is.na(value)) %>%
  group_by(layer, energy_cat) %>%
  summarise(
    area_km2 = sum(area_km2)) %>%
  spread(energy_cat, area_km2)

lims$min_breaks

setNames(  names(tbl_long[-1]))
c()
rename_at()

View(tbl_long)
range(tbl_long$value)

  
  select(-depth, )
table(tbl$energy_cat)
names(tbl)
```