---
output:
  html_document:
    df_print: paged
    number_sections: true
    toc: true
    toc_float: true    
  word_document:
    fig_caption: yes
    reference_docx: ~/Google Drive/projects/nrel-ecoquants/docs/nrel-uses_parts/nrel_fmt4rmd.docx
---

# Appendix

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=F, message=F, eval=T, echo=F, cache=F)
options(knitr.kable.NA = '')

source(here::here("scripts/setup.R"))
devtools::load_all(here("../nrelutils"))

i_tbl <<- 0
src <- NULL

# iterate over territories and bins
territories <- eez_s05_wgcs_sf$territory
#territories <- c("Alaska", "Atlantic Islands", "East", "Great Lakes", "Gulf of Mexico", "Hawaii", "Pacific Islands", "West")
#territories <- c("Hawaii")
bins <- names(limits)
#bins <- "depth"

# TODO: Appendix by region of outputs

for (ter in territories){ # ter = "Hawaii" # territories[1] # "Alaska" # "Atlantic Islands" # territories[1]
  msg(g("{ter}"))
  
  src <- c(src, glue("

## {ter}

```{{r {ter}}}
ter <- '{ter}'
```"))
  
  ter_info  <- make_ter_info(ter, lyr_params, bins)

  # TODO: mask(), crop(), raster_trim() at lyr prep; extend() at ter_stack_r()
#   Hawaii  - 2018-01-08 07:32:14 
#   missing or redo layer oceanuseatlas.orwa, but not in Hawaii, so ter_info$layers$oceanuseatlas.orwa = NA  - 2018-01-08 07:32:14 
#   missing_layers: oceanuseatlas.hi  - 2018-01-08 07:32:14 
#   missing_types :   - 2018-01-08 07:32:14 
#   loading ter_s, ter_s_tbl  - 2018-01-08 07:32:14 
#     Hawaii - aquaculture  - 2018-01-08 07:32:14 
#     Hawaii - depth  - 2018-01-08 07:32:14 
#     Hawaii - mpa  - 2018-01-08 07:32:14 
#     Hawaii - oceanuseatlas.hi  - 2018-01-08 07:32:14 
# Quitting from lines 20-114 (nrel-uses.Rmd) 
#  Hide Traceback
#  
#  Rerun with Debug
#  Error in compareRaster(x) : different extent 
  
  src <- c(src, glue("

### {ter}: Map of Uses

```{{r map{ter}, fig.cap=\"{map_ter_caption(ter, 'all', 'count')}\"}}
map_ter(ter, 'all', 'count')
```"))
  
  for (bin in bins){ # bin = bins[1]
    
    if (is.na(ter_info[[bin]][1])) next
    
    bin_cap  <- stringr::str_to_title(bin)
    bin_html    <- lyr_params %>% 
      filter(key == bin) %>%
      .$title
    
    src <- c(src, glue("

```{{r {ter}-{bin}}}
bin         <- '{bin}'
bin_cap     <- '{bin_cap}'
bin_html    <- '{bin_html}'
```"))
    # TODO: fix Inf in: "The total area considered was limited to maximum depth of 100 m and minimum tide of Inf W/m2"
    # TODO: append units, eg (m/s) to "viable {bin}"
    # TODO: fix W/m2 to W/m^2^, km2 to km^2^
    # TODO: Yeah, the red areas in the "East: Map of Uses" are hard to see because the region is so big. Would make sense to break up the East region into the 3 regional planning bodies as discussed in section "1.1 Context of Marine Spatial Planning" per cmsp.noaa.gov/activities (and rename "Atlantic Islands" to "Caribbean"):

    src <- c(src, glue("

### {ter}: Map of {bin_cap}

```{{r map{ter}{bin}, fig.cap=\"{map_ter_caption(ter, bin, 'limits')}\"}}
map_ter(ter, bin, 'limits')
```"))

    src <- c(src, glue("

### {ter}: Plot of Uses by {bin_cap}

```{{r fig{ter}{bin}, fig.cap='{plot_caption_ter_bin_cnt(ter, bin_html)}'}}
plot_ter_bin_cnt(ter, bin)
```"))
    
    src <- c(src, glue("

### {ter}: Table of Uses by {bin_cap}

```{{r tbl{ter}{bin}}}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```"))

  }
}

src <- glue("{src}\n")
write_lines(src, here("docs/nrel-uses_appendix-src.Rmd"))
res = knit_child(text = unlist(src))
```

```{r knitted_result, results="asis", eval=T}
cat(paste(res, collapse = "\n"))
```
