
## Alaska

```{r Alaska}
ter <- 'Alaska'
```

### Alaska: Map of Uses

```{r mapAlaska, fig.cap="Map of cumulative ocean use in Alaska region."}
map_ter(ter, 'all', 'count')
```

```{r Alaska-depth}
bin         <- 'depth'
bin_cap     <- 'Depth'
bin_html    <- 'Depth (m)'
```

### Alaska: Map of Depth

```{r mapAlaskadepth, fig.cap="Map of viable depth in Alaska region."}
map_ter(ter, bin, 'limits')
```

### Alaska: Plot of Uses by Depth

```{r figAlaskadepth, fig.cap='Area of Cumulative Ocean Use by Depth (m) for Alaska region. Cumulative use are counted and summarized by Depth (m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Alaska: Table of Uses by Depth

```{r tblAlaskadepth}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r Alaska-tide}
bin         <- 'tide'
bin_cap     <- 'Tide'
bin_html    <- 'Tide (W/m2)'
```

### Alaska: Map of Tide

```{r mapAlaskatide, fig.cap="Map of viable tide in Alaska region."}
map_ter(ter, bin, 'limits')
```

### Alaska: Plot of Uses by Tide

```{r figAlaskatide, fig.cap='Area of Cumulative Ocean Use by Tide (W/m2) for Alaska region. Cumulative use are counted and summarized by Tide (W/m2) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Alaska: Table of Uses by Tide

```{r tblAlaskatide}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r Alaska-wave}
bin         <- 'wave'
bin_cap     <- 'Wave'
bin_html    <- 'Wave (kW/m)'
```

### Alaska: Map of Wave

```{r mapAlaskawave, fig.cap="Map of viable wave in Alaska region."}
map_ter(ter, bin, 'limits')
```

### Alaska: Plot of Uses by Wave

```{r figAlaskawave, fig.cap='Area of Cumulative Ocean Use by Wave (kW/m) for Alaska region. Cumulative use are counted and summarized by Wave (kW/m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Alaska: Table of Uses by Wave

```{r tblAlaskawave}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

## Atlantic Islands

```{r Atlantic Islands}
ter <- 'Atlantic Islands'
```

### Atlantic Islands: Map of Uses

```{r mapAtlantic Islands, fig.cap="Map of cumulative ocean use in Atlantic Islands region."}
map_ter(ter, 'all', 'count')
```

```{r Atlantic Islands-depth}
bin         <- 'depth'
bin_cap     <- 'Depth'
bin_html    <- 'Depth (m)'
```

### Atlantic Islands: Map of Depth

```{r mapAtlantic Islandsdepth, fig.cap="Map of viable depth in Atlantic Islands region."}
map_ter(ter, bin, 'limits')
```

### Atlantic Islands: Plot of Uses by Depth

```{r figAtlantic Islandsdepth, fig.cap='Area of Cumulative Ocean Use by Depth (m) for Atlantic Islands region. Cumulative use are counted and summarized by Depth (m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Atlantic Islands: Table of Uses by Depth

```{r tblAtlantic Islandsdepth}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r Atlantic Islands-wave}
bin         <- 'wave'
bin_cap     <- 'Wave'
bin_html    <- 'Wave (kW/m)'
```

### Atlantic Islands: Map of Wave

```{r mapAtlantic Islandswave, fig.cap="Map of viable wave in Atlantic Islands region."}
map_ter(ter, bin, 'limits')
```

### Atlantic Islands: Plot of Uses by Wave

```{r figAtlantic Islandswave, fig.cap='Area of Cumulative Ocean Use by Wave (kW/m) for Atlantic Islands region. Cumulative use are counted and summarized by Wave (kW/m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Atlantic Islands: Table of Uses by Wave

```{r tblAtlantic Islandswave}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

## East

```{r East}
ter <- 'East'
```

### East: Map of Uses

```{r mapEast, fig.cap="Map of cumulative ocean use in East region."}
map_ter(ter, 'all', 'count')
```

```{r East-depth}
bin         <- 'depth'
bin_cap     <- 'Depth'
bin_html    <- 'Depth (m)'
```

### East: Map of Depth

```{r mapEastdepth, fig.cap="Map of viable depth in East region."}
map_ter(ter, bin, 'limits')
```

### East: Plot of Uses by Depth

```{r figEastdepth, fig.cap='Area of Cumulative Ocean Use by Depth (m) for East region. Cumulative use are counted and summarized by Depth (m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### East: Table of Uses by Depth

```{r tblEastdepth}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r East-tide}
bin         <- 'tide'
bin_cap     <- 'Tide'
bin_html    <- 'Tide (W/m2)'
```

### East: Map of Tide

```{r mapEasttide, fig.cap="Map of viable tide in East region."}
map_ter(ter, bin, 'limits')
```

### East: Plot of Uses by Tide

```{r figEasttide, fig.cap='Area of Cumulative Ocean Use by Tide (W/m2) for East region. Cumulative use are counted and summarized by Tide (W/m2) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### East: Table of Uses by Tide

```{r tblEasttide}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r East-wave}
bin         <- 'wave'
bin_cap     <- 'Wave'
bin_html    <- 'Wave (kW/m)'
```

### East: Map of Wave

```{r mapEastwave, fig.cap="Map of viable wave in East region."}
map_ter(ter, bin, 'limits')
```

### East: Plot of Uses by Wave

```{r figEastwave, fig.cap='Area of Cumulative Ocean Use by Wave (kW/m) for East region. Cumulative use are counted and summarized by Wave (kW/m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### East: Table of Uses by Wave

```{r tblEastwave}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r East-wind}
bin         <- 'wind'
bin_cap     <- 'Wind'
bin_html    <- 'Wind (m/s @ 90m)'
```

### East: Map of Wind

```{r mapEastwind, fig.cap="Map of viable wind in East region."}
map_ter(ter, bin, 'limits')
```

### East: Plot of Uses by Wind

```{r figEastwind, fig.cap='Area of Cumulative Ocean Use by Wind (m/s @ 90m) for East region. Cumulative use are counted and summarized by Wind (m/s @ 90m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### East: Table of Uses by Wind

```{r tblEastwind}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

## Great Lakes

```{r Great Lakes}
ter <- 'Great Lakes'
```

### Great Lakes: Map of Uses

```{r mapGreat Lakes, fig.cap="Map of cumulative ocean use in Great Lakes region."}
map_ter(ter, 'all', 'count')
```

```{r Great Lakes-depth}
bin         <- 'depth'
bin_cap     <- 'Depth'
bin_html    <- 'Depth (m)'
```

### Great Lakes: Map of Depth

```{r mapGreat Lakesdepth, fig.cap="Map of viable depth in Great Lakes region."}
map_ter(ter, bin, 'limits')
```

### Great Lakes: Plot of Uses by Depth

```{r figGreat Lakesdepth, fig.cap='Area of Cumulative Ocean Use by Depth (m) for Great Lakes region. Cumulative use are counted and summarized by Depth (m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Great Lakes: Table of Uses by Depth

```{r tblGreat Lakesdepth}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r Great Lakes-wind}
bin         <- 'wind'
bin_cap     <- 'Wind'
bin_html    <- 'Wind (m/s @ 90m)'
```

### Great Lakes: Map of Wind

```{r mapGreat Lakeswind, fig.cap="Map of viable wind in Great Lakes region."}
map_ter(ter, bin, 'limits')
```

### Great Lakes: Plot of Uses by Wind

```{r figGreat Lakeswind, fig.cap='Area of Cumulative Ocean Use by Wind (m/s @ 90m) for Great Lakes region. Cumulative use are counted and summarized by Wind (m/s @ 90m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Great Lakes: Table of Uses by Wind

```{r tblGreat Lakeswind}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

## Gulf of Mexico

```{r Gulf of Mexico}
ter <- 'Gulf of Mexico'
```

### Gulf of Mexico: Map of Uses

```{r mapGulf of Mexico, fig.cap="Map of cumulative ocean use in Gulf of Mexico region."}
map_ter(ter, 'all', 'count')
```

```{r Gulf of Mexico-depth}
bin         <- 'depth'
bin_cap     <- 'Depth'
bin_html    <- 'Depth (m)'
```

### Gulf of Mexico: Map of Depth

```{r mapGulf of Mexicodepth, fig.cap="Map of viable depth in Gulf of Mexico region."}
map_ter(ter, bin, 'limits')
```

### Gulf of Mexico: Plot of Uses by Depth

```{r figGulf of Mexicodepth, fig.cap='Area of Cumulative Ocean Use by Depth (m) for Gulf of Mexico region. Cumulative use are counted and summarized by Depth (m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Gulf of Mexico: Table of Uses by Depth

```{r tblGulf of Mexicodepth}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r Gulf of Mexico-tide}
bin         <- 'tide'
bin_cap     <- 'Tide'
bin_html    <- 'Tide (W/m2)'
```

### Gulf of Mexico: Map of Tide

```{r mapGulf of Mexicotide, fig.cap="Map of viable tide in Gulf of Mexico region."}
map_ter(ter, bin, 'limits')
```

### Gulf of Mexico: Plot of Uses by Tide

```{r figGulf of Mexicotide, fig.cap='Area of Cumulative Ocean Use by Tide (W/m2) for Gulf of Mexico region. Cumulative use are counted and summarized by Tide (W/m2) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Gulf of Mexico: Table of Uses by Tide

```{r tblGulf of Mexicotide}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r Gulf of Mexico-wind}
bin         <- 'wind'
bin_cap     <- 'Wind'
bin_html    <- 'Wind (m/s @ 90m)'
```

### Gulf of Mexico: Map of Wind

```{r mapGulf of Mexicowind, fig.cap="Map of viable wind in Gulf of Mexico region."}
map_ter(ter, bin, 'limits')
```

### Gulf of Mexico: Plot of Uses by Wind

```{r figGulf of Mexicowind, fig.cap='Area of Cumulative Ocean Use by Wind (m/s @ 90m) for Gulf of Mexico region. Cumulative use are counted and summarized by Wind (m/s @ 90m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Gulf of Mexico: Table of Uses by Wind

```{r tblGulf of Mexicowind}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

## Hawaii

```{r Hawaii}
ter <- 'Hawaii'
```

### Hawaii: Map of Uses

```{r mapHawaii, fig.cap="Map of cumulative ocean use in Hawaii region."}
map_ter(ter, 'all', 'count')
```

```{r Hawaii-depth}
bin         <- 'depth'
bin_cap     <- 'Depth'
bin_html    <- 'Depth (m)'
```

### Hawaii: Map of Depth

```{r mapHawaiidepth, fig.cap="Map of viable depth in Hawaii region."}
map_ter(ter, bin, 'limits')
```

### Hawaii: Plot of Uses by Depth

```{r figHawaiidepth, fig.cap='Area of Cumulative Ocean Use by Depth (m) for Hawaii region. Cumulative use are counted and summarized by Depth (m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Hawaii: Table of Uses by Depth

```{r tblHawaiidepth}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r Hawaii-wave}
bin         <- 'wave'
bin_cap     <- 'Wave'
bin_html    <- 'Wave (kW/m)'
```

### Hawaii: Map of Wave

```{r mapHawaiiwave, fig.cap="Map of viable wave in Hawaii region."}
map_ter(ter, bin, 'limits')
```

### Hawaii: Plot of Uses by Wave

```{r figHawaiiwave, fig.cap='Area of Cumulative Ocean Use by Wave (kW/m) for Hawaii region. Cumulative use are counted and summarized by Wave (kW/m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Hawaii: Table of Uses by Wave

```{r tblHawaiiwave}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r Hawaii-wind}
bin         <- 'wind'
bin_cap     <- 'Wind'
bin_html    <- 'Wind (m/s @ 90m)'
```

### Hawaii: Map of Wind

```{r mapHawaiiwind, fig.cap="Map of viable wind in Hawaii region."}
map_ter(ter, bin, 'limits')
```

### Hawaii: Plot of Uses by Wind

```{r figHawaiiwind, fig.cap='Area of Cumulative Ocean Use by Wind (m/s @ 90m) for Hawaii region. Cumulative use are counted and summarized by Wind (m/s @ 90m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Hawaii: Table of Uses by Wind

```{r tblHawaiiwind}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

## Pacific Islands

```{r Pacific Islands}
ter <- 'Pacific Islands'
```

### Pacific Islands: Map of Uses

```{r mapPacific Islands, fig.cap="Map of cumulative ocean use in Pacific Islands region."}
map_ter(ter, 'all', 'count')
```

```{r Pacific Islands-depth}
bin         <- 'depth'
bin_cap     <- 'Depth'
bin_html    <- 'Depth (m)'
```

### Pacific Islands: Map of Depth

```{r mapPacific Islandsdepth, fig.cap="Map of viable depth in Pacific Islands region."}
map_ter(ter, bin, 'limits')
```

### Pacific Islands: Plot of Uses by Depth

```{r figPacific Islandsdepth, fig.cap='Area of Cumulative Ocean Use by Depth (m) for Pacific Islands region. Cumulative use are counted and summarized by Depth (m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### Pacific Islands: Table of Uses by Depth

```{r tblPacific Islandsdepth}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

## West

```{r West}
ter <- 'West'
```

### West: Map of Uses

```{r mapWest, fig.cap="Map of cumulative ocean use in West region."}
map_ter(ter, 'all', 'count')
```

```{r West-depth}
bin         <- 'depth'
bin_cap     <- 'Depth'
bin_html    <- 'Depth (m)'
```

### West: Map of Depth

```{r mapWestdepth, fig.cap="Map of viable depth in West region."}
map_ter(ter, bin, 'limits')
```

### West: Plot of Uses by Depth

```{r figWestdepth, fig.cap='Area of Cumulative Ocean Use by Depth (m) for West region. Cumulative use are counted and summarized by Depth (m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### West: Table of Uses by Depth

```{r tblWestdepth}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r West-tide}
bin         <- 'tide'
bin_cap     <- 'Tide'
bin_html    <- 'Tide (W/m2)'
```

### West: Map of Tide

```{r mapWesttide, fig.cap="Map of viable tide in West region."}
map_ter(ter, bin, 'limits')
```

### West: Plot of Uses by Tide

```{r figWesttide, fig.cap='Area of Cumulative Ocean Use by Tide (W/m2) for West region. Cumulative use are counted and summarized by Tide (W/m2) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### West: Table of Uses by Tide

```{r tblWesttide}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r West-wave}
bin         <- 'wave'
bin_cap     <- 'Wave'
bin_html    <- 'Wave (kW/m)'
```

### West: Map of Wave

```{r mapWestwave, fig.cap="Map of viable wave in West region."}
map_ter(ter, bin, 'limits')
```

### West: Plot of Uses by Wave

```{r figWestwave, fig.cap='Area of Cumulative Ocean Use by Wave (kW/m) for West region. Cumulative use are counted and summarized by Wave (kW/m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### West: Table of Uses by Wave

```{r tblWestwave}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```

```{r West-wind}
bin         <- 'wind'
bin_cap     <- 'Wind'
bin_html    <- 'Wind (m/s @ 90m)'
```

### West: Map of Wind

```{r mapWestwind, fig.cap="Map of viable wind in West region."}
map_ter(ter, bin, 'limits')
```

### West: Plot of Uses by Wind

```{r figWestwind, fig.cap='Area of Cumulative Ocean Use by Wind (m/s @ 90m) for West region. Cumulative use are counted and summarized by Wind (m/s @ 90m) and area.'}
plot_ter_bin_cnt(ter, bin)
```

### West: Table of Uses by Wind

```{r tblWestwind}
tbl_blsp <- ter_bin_lyr_smry_plus(ter, bin, lyr_params, lyr_categories)
print_tbl_ter_bin_lyr_smry_plus(tbl_blsp)
```
